|

### 2025-01-31 doc/paper.qmd
expand dataset window +-1
annual stock data

7. To account for non-trading days in Datastream, I extend the event window from (-1, +1) to (-3, +3) to ensure the inclusion of trading days around earnings announcements.

@@

>>>>

@@

Notably, after pulling the annual stock data for further annual return calculation, all infocodes present an average of 250 trading days, highlighting full year stock coverage.
